Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-18 paper/paper.tex
Integrate DM's comments in the abstract

\begin{abstract}
The default mode network (DMN) is believed to subserve the human
baseline mental activity.
%
Many research streams converge to its likely role in evolutionarily adaptive
envisioning of mental scenarios to simulate the future.
Such functional roles become more likely due to
this brain network's highest energy consumption in the brain and
its intimate coupling with conscious awareness.
%
The present concept paper proposes a \textit{process model}
in trying to explain \textit{how} the DMN may actually implement continuous
assessment and prediction of the environment to guide action choices.
DMN function is recast in the mathematical terms of
control theory and reinforcement learning based on Markov decision processes.
We argue that our formal account of DMN function
naturally accommodates
previously proposed cognitive accounts as special cases and
parsimoniously explains
experimental findings in animals and humans.
%
A process model for the neural implemention
of continuous future predictions potentially realized in the DMN
could offer insight into the statistical mechanisms underlying human behavior.
\end{abstract}

>>>>

\begin{abstract}
The default mode network (DMN) is believed to subserve the human
baseline mental activity.
%
Its highest energy consumption in the brain and
its intimate coupling with conscious awareness are both pointing towards an important functional roles.
%
Many research streams support its evolutionarily adaptive role as
envisioning mental scenarios to simulate the future.

The present concept paper proposes to explain \textit{how} the DMN may actually implement such continuous assessment and prediction of the environment to guide action choices.

DMN function is recast in mathematical terms of
control theory and reinforcement learning based on Markov decision processes.
%
We argue that our formal account of DMN function naturally accommodates as special cases
previously proposed cognitive accounts such as \textit{predictive coding}.
%
A process model for the neural implemention
of continuous future predictions potentially realized in the DMN
could offer insight into the statistical mechanisms underlying human behavior and provide a parsimonious explanation of experimental findings in animals and humans.
\end{abstract}
